%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Arxiu pregenerat.
% NO EDITAR
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Judit Díaz}

I was born in Barcelona, in the afternoon of November 28th, 1995. When I was 2 we moved to our current flat. Before that, we lived in another flat, which was a little bit smaller than this one, but this wasn’t the reason why we moved, it was basically because the new flat had a bigger terrace. I don’t remember anything about our old flat, but I don’t care because I have a lot of memories of this one. For example, when I was younger we celebrated my birthday parties in the terrace, my friends came and my mother prepared a kind of gymkhana with a lot of funny games. I’ll always remember it, at least I hope so.  

My earliest memory is when my sister was born. I was about two and a half years old. I remember that I was in a hospital room with my grandmother, my mother was lying in bed and there was a baby crib next to my mum’s bed. I think there were more people in the room but this part is fuzzy. I love that my earliest memory is that, because I will never forget the first time that I saw my sister.

I also remember the primary school; I had a lot of teachers, one different teacher every year. The truth is that I remember everything of that period of time. I’ve been at Solc School, my school, since I was three. It’s a primary and secondary school, so this is my last year here in this school, and I’m sad because I’ve been seeing the same people every day and I will miss them. 

I’ve changed since I was young, but not a lot. And now my hair has a different colour!

When I finish secondary school I’ll go to the bachelor's degree and after that I’ll probably go to the university.

Before I’m old I really want to travel around the world and visit a lot of places, I’ve never travelled abroad, except from France, and it’s something that I wanted to do long time ago.


\authorandplace{Judit Díaz}{4th ESO}

\end{news}
